---
title: "HW_2poz3615"
author: "Piper Zimmerman"
date: "September 9, 2021"
output: pdf_document
header-includes:
   - \usepackage{enumitem}
---
2.
a. In this class, I am hoping to learn how to use R more proficiently without having to look the majority of what I'm coding up. This is my first time using R Markdown, so I'm excited to get familiar with that. 
```{r}
Objectives<-list("Loops","Data Cleaning","Creating Plots from Loops and Data Analysis")
Objectives
```

b. 
\begin{equation} 
f(x|a,b)=\frac{1}{b-a} \: \: a \leq x\leq b
\end{equation}

\begin{equation}
f(x|\alpha,\beta)=\frac{1}{\Gamma (\alpha)\beta^\alpha} x^{\alpha-1}e^{-\frac{x}{\beta}}\: \: 0 \leq x < \infty,\: \: \alpha,\beta>0
\end{equation}

\begin{equation}
f(x|\beta)=\frac{1}{\beta}e^{\frac{-x}{\beta}} \: \: 0\leq x < \infty, \: \: \beta>0
\end{equation}

3. 
\begin{enumerate}[label=(\arabic*)]
  \item For Every Result, Keep Track of How It Was Produced- Make sure you keep track of anything that might influence how you got a result, such as a parameter or input. A challenge in performing this step could be labeling and keeping everything organized so you know which code gave you which results.
  \item Avoid Manual Data Manipulation Steps- You should rely on the execution of the programs rather than manually modifying data. A challenge in performing this step could be trying to fix something the easy way manually instead of trying to work it out through the program.
  \item Archive the Exact Versions of All External Programs Used- Always keep the version of the program that you used to create the original result. A challenge in performing this step could be if your computer won't run the version of the program anymore.
  \item Version Control All Custom Scripts- Archive all of your codes to ensure that you have the one that gave the intended results. A challenge in performing this step could be keeping the scripts organized and easy to find.
  \item Record All Intermediate Results, When Possible in Standardized Formats- Store all your results on the way as they might be helpful when you are looking back. A challenge in performing this step could be having too many results that they get mixed up and hard to find.
  \item For Analyses That Include Randomness, Note Underlying Random Seeds- If using randomness, the results will vary unless you set the seed the same, so take note of the seed and which steps involve randomness. A challenge in performing this step could be picking out all the steps with randomness. If one is missed, and the seed is not set, it will provide different results.
  \item Always Store Raw Data Behind Plots- Saving raw data behind the plot will reduce time and effort needed to modify the plot in the future. A challenge in performing this step could be keeping the data organized in order to make quick adjustments to the plots.
  \item Generate Hierarchical Analysis Output, Allowing Layers of Increasing Detail to Be Inspected- If you are using summarized results, you should also look at the data that is underlying the summaries. A challenge in performing this step could be if the summarized data doesn't have an option to see the full set.
  \item Connect Textual Statements to Underlying Results- It is important to have more than just the interpretations in text on a paper. The data and results should be easily accessible. A challenge in performing this step could be finding a way to make the data accessible while preserving the professionalism of the paper and not straying from the topic at hand.
  \item Provide Public Access to Scripts, Runs, and Results- Everything should be made public and easily accessible, including the data and source code. A challenge in performing this step could be making everything easily accessible and organized.
\end{enumerate}

4. 
```{r}
library(data.table)
library(curl)
covid_raw <- fread("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
us <- covid_raw[covid_raw$countriesAndTerritories == 'United_States_of_America',]
us_filtered <- us[us$month %in% c(6:7),]
us_filtered$index <- rev(1:dim(us_filtered)[1]) 
fit<-lm(`Cumulative_number_for_14_days_of_COVID-19_cases_per_100000`~index, data=us_filtered)
```
ai.
``` {r}
library(knitr)
kable(summary(us_filtered))
```
There are missing values. We have limited ourselves to 61 time points.

aii. 
```{r}
library(stargazer)
stargazer(fit)
```
\begin{table}[!htbp] \centering
\caption{}
\label{}
\begin{tabular}{@{\extracolsep{5pt}}lc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
& \multicolumn{1}{c}{\textit{Dependent variable:}} \\
\cline{2-2}
\\[-1.8ex] &`Cumulative\_number\_for\_14\_days\_of\_COVID-19\_cases\_per\_100000`\\
\hline \\[-1.8ex]
index & 4.107$^{***}$ \\
& (0.145) \\
& \\
Constant & 42.853$^{***}$ \\
& (5.165) \\
& \\
\hline \\[-1.8ex]
Observations & 61 \\
R$^{2}$ & 0.932 \\
Adjusted R$^{2}$ & 0.930 \\
Residual Std. Error & 19.922 (df = 59) \\
F Statistic & 803.464$^{***}$ (df = 1; 59) \\
\hline
\hline \\[-1.8ex]
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
\end{tabular} 
\end{table}

b.
```{r}
library(broom)
fit.diags <- broom::augment(fit)
par(mfrow=c(2,2))
plot(fit.diags$.fitted,fit.diags$.resid, main="Residual vs Fitted")
plot(fit.diags$.fitted,sqrt(abs(fit.diags$.std.resid)),main="Normal Q-Q")
qqnorm(fit.diags$.std.resid, main="Scale-Location")
plot(fit.diags$.hat,fit.diags$.std.resid, main="Residuals vs Leverage")
```
c.
```{r}
acf(fit$residuals,main="ACF Plot")
```



